Introducing the \NAME Framework\\ for Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-06 paper.tex
started describing the background of FCF with algo

\documentclass[conference]{IEEEtran}
\usepackage[pdftex]{graphicx}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{algorithmic}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{url}
\hyphenation{}

@@

\usepackage{lineno}
\setlength\linenumbersep{1mm}
\linenumbers

@@

@@

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[pdftex]{graphicx}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
% \usepackage{algorithmic}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{url}
\hyphenation{}

@@

% while preparing, linenumbers come in handy
\usepackage{lineno}
\setlength\linenumbersep{1mm}
\linenumbers

@@

% http://tex.stackexchange.com/questions/299/how-to-get-long-texttt-sections-to-break
\newcommand*\justify{%
  \fontdimen2\font=0.4em% interword space
  \fontdimen3\font=0.2em% interword stretch
  \fontdimen4\font=0.1em% interword shrink
  \fontdimen7\font=0.1em% extra space
  \hyphenchar\font=`\-% allowing hyphenation
}

% http://en.wikibooks.org/wiki/LaTeX/Customizing_LaTeX
\newcommand{\ttt}[1]{\texttt{\justify{#1}}}

\usepackage{algpseudocode}
% custom Let command
\newcommand*\Let[2]{\State #1 $\gets$ #2}
\renewcommand{\algorithmicforall}{\textbf{for each}}
\let\ForEach\ForAll

@@

ID algorithms targeting MANETs share a common design pattern as illustrated in
pseudocode listing \ref{alg:id-algo-pattern}. It consists of two functions:
\ttt{process\_message} and \ttt{do\_housekeeping}. The former function
represents the fact that ID algorithms inspect the network traffic that is
captured by the wireless radio and process it, looking for malicious activity.
The latter allows for algorithms to perform periodical tasks, checking their
internal information and optionally act upon it. Some algorithms will implement
both functions, some don't, but the abstract structure is applicable for a
significant number of algorithms.

\begin{listing}
\begin{algorithmic}[1]
  \Require{nodes, global storage for information about nodes}
  \Function{process\_message}{$msg$}
    \ForEach{$byte \in msg$} \label{alg:id-algo-pattern-loop1}
     \State \dots \Comment{analyse byte-sequences}
    \EndFor
    \Let{$nodes_x$}{value}  \Comment{optionally update node info}
    \State \Call{send}{$nodes_y$, ``info''} \Comment{optionally exchange info} \label{alg:id-algo-pattern-send}
  \EndFunction
  \State
  \Function{do\_housekeeping}{}
    \ForEach{$node \in nodes$} \label{alg:id-algo-pattern-loop2}
      \If{$node > \dots$} \Comment{validate recorded value}
        \State \dots \Comment{take actions}
      \EndIf
    \EndFor
  \EndFunction
  \State
\end{algorithmic}
\caption{ID Algorithm Pattern\label{alg:id-algo-pattern}}
\end{listing}

The parts of interest here the iterations at lines
\ref{alg:id-algo-pattern-loop1} and \ref{alg:id-algo-pattern-loop2}, and the
interaction with the network at line \ref{alg:id-algo-pattern-send}.
